---
title: "Homework 0"
author: Shirley(Xueying) Chen
format: html
execute:
  echo: FALSE
---

```{r}
# Assign values to a, b, and c here:
a <- 1
b <- 3
c <- 2
```

**Showing the solution(s) to the quadratic equation**

After assigning values to a, b, and c, we use the 
the quadratic formula to calculate the solution(s). 
$$ x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$$
We first calculate $b^2 -4ac$ to check if it is larger or greater than 0 (whether or not the equation has a solution).

```{r}
val <- b^2-4*a*c
```
From the calculated value (which equals to `r val`), we can further use the quadratic formula to calculate the solution (if there is one).

```{r, warning= FALSE}
# using if-else statements to print out the corresponding solutions regarding the a, b, and c values plugged in above. 
if (val < 0) { 
  print('There is no solution to the equation.') # if val is less than 0, which means there is no solution to the equation. 
}else if (val == 0) {
  print(paste('There is one solution:' , as.character((-b+sqrt(b^2 - 4*a*c))/2*a))) # if val equals to 0, which means there is only one solution.
}else {
  print(paste('There are two solutions:', as.character((-b+sqrt(b^2 - 4*a*c))/2*a),', ', as.character((-b-sqrt(b^2 - 4*a*c))/2*a) )) # if val is greater than 0, the equation has two distinct solutions. 
  
}
```

**Plotting the quadratic curve with the line y = 0 for** $$x\in (-5, 5)$$

```{r}
# assigning x to a range of -5 to 5 giving the length of the sequence to be 300.
x <- seq(-5,5,length = 300)
# plotting the quadratic curve
plot(x, a*x^2 + b*x + c, type = "l")
# adding a horizontal line passing y = 0. The intersection with the quadratic curve confirms the solutions calculated above.  
abline(h = 0, lty = 2)
```
